---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# sitreper

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/sitreper)](https://cran.r-project.org/package=sitreper)
<!-- badges: end -->

The goal of `sitreper` is to provide a multiple set of functions for the generation of situational reports:

- space-time tibble delimiters based on epidemiological weeks
- geocode places within a tibble
- surveillance specific cleaning tools
- visually sumarized who-sitrep-covid19

## Installation

<!--

You can install the released version of `sitreper` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sitreper")
```

-->

You can install the development version of `sitreper` using:

``` r
if(!require("devtools")) install.packages("devtools")
devtools::install_github("cdcperu/sitreper")
```


## Example

This is a basic example which shows you how to solve a common problem:

### geocode

```r
library(opencage)
library(tidyverse)
library(sitreper)

opencagekey <- "paste_free_geocode_key_here"

# examples ----------------------------------------------------------------

place_01 <- "Calle Daniel Olaechea 199, LIMA PERU"
place_02 <- "Ministerio de Salud Lima Peru"
place_03 <- "Av. Salaverry 801, Jesus Maria 15072"
place_10 <- "Sarzeau"

data_query <- tibble(place=c(place_01,place_02,place_03,place_10))

data_query %>%
  sitrep_opencage_tidy_map(place = place,opencagekey = opencagekey)
#> # A tibble: 3 x 8
#>   place geocode geometry.lat geometry.lng confidence components.post~
#>   <chr> <list>         <dbl>        <dbl> <fct>      <fct>
#> 1 Call~ <tibbl~        -12.1        -77.0 9          15072
#> 2 Mini~ <tibbl~        -12.1        -77.0 10         LIMA 15046
#> 3 Av. ~ <tibbl~        -12.1        -77.0 10         LIMA 15046
#> # ... with 2 more variables: components._category <fct>,
#> #   annotations.OSM.url <fct>

```

### who sitrep covid-19

```{r,fig.height=7.5,fig.width=9}
library(sitreper)

#paste
path_file <- "https://raw.github.com/fkrauer/COVID-19/master/data/WHO_COVID19_ALL_ADM0_2020-03-10.csv"

#apply
who_sitrep_country_report(
  data_input = path_file,
  country = "Brazil")
```

